% % LaTeX resume using res.cls
\documentclass[line, margin]{res}
% \usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
% \usepackage{newcent}   % uses new century schoolbook postscript font
% \setlength{\textwidth}{5.1in} % set width of text portion

\begin{document}

% Center the name over the entire width of resume:
% \moveleft.5\hoffset\centerline{\large\bf Cameron D. Pelkey}
% \moveleft.5\hoffset\centerline{cameron.pelkey@gmail.com}
% Draw a horizontal line the whole width of resume:
% address begins here
% Again, the address lines must be centered over entire width of resume:
\name{Cameron D. Pelkey}
\address{4607 N Sheridan Rd Apt 204, Chicago, IL 60640}
\address{Cell: 571.337.9654, Email: cameron.pelkey@gmail.com}


\begin{resume}

\section{OBJECTIVE}  A full-time development position with particular focus in information processing and applications programming.


\section{EDUCATION} {\sl Bachelor of Science,} Computer Science \hfill \textbf{May 2014}\\
		George Mason University, Fairfax, VA\\
		Concentration: Computer Science \\
		GPA 3.18


% \section{COURSEWORK}
%     \begin{ncolumn}{2}
%         Operating systems & Language Processing \& Analysys \\
%         Python, Java, C/Assembly & Software Project Management \\
%         Artificial Intelligence \& Metaheuristics
%     \end{ncolumn}


\section{WORK \\ EXPERIENCE}
    \textbf{Software Implementation Technical Practitioner \hfill September 2014 - \\\hspace*{\fill}October 2016\hspace*{8px}}\\
    Accenture Federal Services
    \begin{itemize}  \itemsep -2pt %reduce space between items
        \item Led day-to-day efforts in maintaining and improving archiving effectiveness.
        \item Designed and led effort to upgrade OpenText archiving systems throughout Sandbox, Development, and Production landscapes.
        \item Worked closely with software vendors in developing and implementing solutions to resolve issues in a timely manner.
        \item Created and maintained internal documentation of various internal systems and maintenance methodologies.
    \end{itemize}
	\textbf{Academic Researcher \hfill January 2013 - September 2014} \\
	Laboratory for Games and Intelligent Animation (GAIA), George Mason University
	\begin{itemize}  \itemsep -2pt %reduce space between items
		\item Assisted in research concerning the development of virtual humans and their behavior within a virtual environment.
		\item Designed and implemented a modular system for the injection of natural language semantics into a virtual environment with funding from the Undergraduate Research Scholars Program, a competitive internal grant at Mason.
	\end{itemize}
	\textbf{Undergraduate Teaching Assistant \hfill 2011, September 2012 - May 2014} \\
	Computer Science Department, George Mason University
	\begin{itemize}  \itemsep -2pt %reduce space between items
		\item Assisted Graduate Teaching Assistants in presenting CS112 and CS211 course material in Python and Java, respectively.
		\item Presented quizzes in lab.
		\item Assisted in proctoring midterm and final exams.
		\item Assisted students both during lab as well as individually outside of lab.
	\end{itemize}

\section{PROJECTS}
    \textbf{Language Processing \hfill 2014 }
    \begin{itemize}  \itemsep -2pt %reduce space between items
        \item Developed a compiler for a subset of the Tiger programming language. Implementation included a lexer, a parser, a functioning type system, and functional assembly code generation.
    \end{itemize}
    \textbf{Information Security \& Encryption \hfill 2013 }
    \begin{itemize}  \itemsep -2pt %reduce space between items
        \item Designed and implemented a proof of concept program for copy-resistant, desktop photo-sharing.
    \end{itemize}\textbf{Computer Vision \hfill 2013 }
    \begin{itemize}  \itemsep -2pt %reduce space between items
        \item Designed and implemented and efficient method for mapping highly articulate image objects to facial key points in real-time using Microsoft’s Kinect technology.
    \end{itemize}
    % \textbf{Open Source \hfill 2012 }
    % \begin{itemize}  \itemsep -2pt %reduce space between items
    %     \item Designed and implemented improvements to Violet-UML using a variety of build tools (including GNU Make and Apache Maven). Implementation included extensive use of Java Enterprise Edition.
    % \end{itemize}

\section{PUBLICATIONS}
	Pelkey, C. and Allbeck, J.M. Populating Virtual Semantic Environments. Computer Animation and Virtual Worlds Journal. Vol. 24 Iss. 3-4, pp. 405-412, May 2014.\vspace{5pt}
	Pelkey, C. and Allbeck, J.M. Injecting Semantic Representation in a Virtual Environment. National Conference on Undergraduate Research, 2014.

\section{HONORS}
	George Mason Honors College Program \hfill \textbf{Fall 2010 - Spring 2014}	\\
	Intensive Undergraduate Research Scholars Program \hfill \textbf{Summer 2013}	\\
	Dean's List of Distinguished Students \hfill \textbf{Fall 2010}	\\
	International Baccalaureate Diploma \hfill \textbf{Spring 2010}			\\

\section{SKILLS}
    {\sl Languages \& Software:} \begin{minipage}[t]{\textwidth}
    C, C++, Java, Python, SQL, Bash, HTML, CSS, \LaTeX, Git,\\
    Subversion, UML, Eclipse, Microsoft Visual Studio, Xcode, \\
    PyCharm, Vim, GDB, NLTK, Lex \& Yacc
    \end{minipage}
    {\sl Operating Systems:} \begin{minipage}[t]{\textwidth}
    Windows, Unix.
    \end{minipage}


\end{resume}
\end{document}




